\vfill A Testing Framework for Web Applications

### 2014-02-13 Paper/paper.tex
Paper: General outline of frameworks/tools section. Implementation: Outline of Jasmine suite, much more info needed for figuring out how to successfully setup testing.

>>>>

\section{Sample App and Testing Frameworks}

\subsection{Sample ToDo App}
In order to test out the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our evaluation application. After some searching, I decided upon a Todo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} This application was selected because it included Node.js and had enough functionality that tests wouldn't be completely trivial while also not being overwhelming.

\subsection{Unit Testing Frameworks}
\subsubsection{Jasmine}
BDD
Had to use jasmine-node (npm install jasmine-node)

\subsubsection{Mocha}

\subsubsection{QUnit}

\subsubsection{Intern}

\subsection{Continuous Integration Frameworks}
\subsubsection{Jenkins}

\subsubsection{Travis}

\subsubsection{Selenium}

\subsubsection{Semaphore}

\subsubsection{Nightwatchjs}

\subsection{Misc Frameworks}
\subsubsection{Sauce Labs}

\subsubsection{Istanbul}

\subsubsection{Karma}

\subsection{Misc Tools}
\subsection{Node Inspector}
Fantastic for debugging node.js server-side code!
